\propertitle

### 2019-06-12 maxNt_v5.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-06-11T15:22:46+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal population\\ from subpopulation data%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

***

Experimental technologies to record the activity of many neurons at the
same time in different species and brain areas are rapidly advancing. These
experimental advancements are paralleled by advances in theoretical and
computational methods for analyzing the data accumulated using the
recording technologies. Such theoretical methods usually take the form of
probabilistic models that try to describe the multi-neuronal activity of
the recorded neurons. With such probabilistic models one aims to address
numerous issues: What correlations are important in describing the
multi-neuronal pattern? How does the pattern of activity covary with
external stimuli or experimental conditions? What dimensionality does the
neural data live in and how is this related to the underlying network
interactions? The probabilistic models can also be used to make predictions
about the structure of the neural code, by studying the properties of the
fitted model, or by generating synthetic data from it.

\mynote{Luca: add this: from sampling theory we know that important
  features of the full network may not be visible in a sample because
  smoothed out. But using sampling theory in the inverse direction we can
  infer such full-network features from the sample.}

@@

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-06-12T11:01:28+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal population\\ from subpopulation data%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

\mynote{Add this?: from sampling theory we know that important
  features of the full network may not be visible in a sample because
  smoothed out. But using sampling theory in the inverse direction we can
  infer such full-network features from the sample.}

\mynote{To be continued after structure of the rest of the article is
  clear. Orig intro is on p.~\pageref{orig_intro}}

@@

\clearpage

\hrule
\newcounter{dummy}\refstepcounter{dummy}\label{orig_intro}
\mynote{orig intro}
Experimental technologies to record the activity of many neurons at the
same time in different species and brain areas are rapidly advancing. These
experimental advancements are paralleled by advances in theoretical and
computational methods for analyzing the data accumulated using the
recording technologies. Such theoretical methods usually take the form of
probabilistic models that try to describe the multi-neuronal activity of
the recorded neurons. With such probabilistic models one aims to address
numerous issues: What correlations are important in describing the
multi-neuronal pattern? How does the pattern of activity covary with
external stimuli or experimental conditions? What dimensionality does the
neural data live in and how is this related to the underlying network
interactions? The probabilistic models can also be used to make predictions
about the structure of the neural code, by studying the properties of the
fitted model, or by generating synthetic data from it.
